Predicting the PCG PSeudo-Random Number Generator In Practice

### 2020-05-20 article/main.tex
retouche + preuve cas dur

We decompose \(U = T + (T-U)\) where \(T\) contains only the upper bits and \(T-U\) the lowers one. There is no reason for \(T\) to be in the lattice, but as \(T-U\) is small, we know \(T\) is \emph{close} to \(U\). So, to find \(U\), we will solve CVP(\(L(\alpha,M,n)\),\(T\)).

\subsection{A first way to solve the CVP : Babai's Round-off Algorithm}

@@

If we can prove that the left side \todo{right side?} of the inequality is smaller than the SVP of G, then wa have proved that \(rG\) is indeed the vector we were searching for.

@@

>>>>

We decompose \(U = T + (T-U)\) where \(T\) contains only the upper bits and \(T-U\) the lowers one. There is no reason for \(T\) to be in the lattice, but as \(T-U\) is small, we know \(T\) is \emph{close} to \(U\).

\subsection{A first way to find U : the Babai's rounding}

@@

If we can prove that the right side \todo{je confonds ma gauche et ma droite et je vous zut :p} of the inequality is smaller than the SVP of G, then wa have proved that \(rG\) is indeed the vector we were searching for.

 \subsection{A second way to find U : using an exact CVP solver}

Solving exactly the CVP is a hard computational problem. But as we do not manipulate quantities too big, we still can use an exact CVP solver.

We know that \(U\) is in the lattice, \(T\) is not and \(|T-U|\) is small. Then we can hope for \(U\) to be the closet vector of \(T\) which is in the lattice : the vector \(U\) may be the solution of \(CVP(L(\alpha,M,n),T)\).

What can we say about \(|CVP(L(\alpha,M,n),T)-U|\) ?

\begin{align*}
|CVP(L(\alpha,M,n),T)-U| &= |CVP(L(\alpha,M,n),T)-T+T-U|\\
& \leqslant |CVP(L(\alpha,M,n),T)-T|+|T-U|\\
\end{align*}

But, as the vector \(U\) is in the lattice and by definition of the CVP, \(|CVP(L(\alpha,M,n),T)-T| \leqslant |T-U| \), hence 
\[|CVP(L(\alpha,M,n),T)-U|\leqslant 2|T-U|\]

If we can prove that the right side of the inequality is smaller than the SVP of the lattice, then wa have proved that \(CVP(L(\alpha,M,n),T)\) is indeed the vector we were searching for.

@@

\subsection{preuve cas difficile}
\todo{À ranger au bon endroit}
% Babai ça marche pas (genre zero)

We call \(U\) the truncated vector : \(S'[\ell,128]\). We notice that \(U\) is in \(L(A,2^{128-\ell},n)\).

We consider the case were we successfully guessed the 6 upper bits of each \(S_i\) and the \(\ell\) lower bits of \(S_0\). Then we know the 6 upper bits of \(U\).

We consider the vector \(T'\) computed in step (numerodelastepenquestion). To recover \(U\), we use an exact CVP solver as explain in  (insererlasection) on \(T'\) and \(L(A,2^{128-\ell},n)\).

As \(U\) and \(T'\) have exactly the same \(6\) upper bits  know that \(\lVert U-T \rVert \leqslant \sqrt{n2^{2(128-6-\ell)}}\).

\[2\sqrt{n}^{(128-6-\ell)} \leqslant \lVert SVP(L(A,2^{128-\ell},n))\rVert \]

\begin{itemize}
	\item For \(\ell=11\), the smallest \(n\) we need is 39.

	\item For \(\ell=12\), the smallest \(n\) we need is 38.

	\item For \(\ell=13\), the smallest \(n\) we need is again 38 .

\end{itemize}
